---
title: "Quick noteson psychoacoustics"
author: "G.Fraga Gonzalez"
date: "`r Sys.Date()`"
output:
  html_document :
    code_folding: hide
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
runhead: Psychoacoustics
abstract: 'Here I collect basic concepts and simple demos on psychoacoustics'
editor_options: 
  markdown: 
    wrap: 72
---

<!-- To unfold code in specific chunks use Chunk options: class.source = 'fold-show' -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gridExtra)
library(dplyr)
library(plotly)
library(ggplot2)
library(nomnoml)
library(DiagrammeR)
library(DT) # for saving tables
```

<!-- ## Intro {.tabset} -->

## Introduction

Psychoacoustics models the relation between acoustic (physics of sound)
and how we perceive sounds (psychology of sound). A good introductory
course is offered byy Bernhard Seeber in <https://youtu.be/7WewuDp171Q>

### Key concepts 

**Loudness** (sound preassure), **roughness** (fluctuation strength),
**masking** (related to differentiating one sound from others),
**critical bands** (frequency sensitivity), **pitch** (strength,
timber).

## Thresholds

xxx
 https://github.com/pmcharrison/parn94
https://cran.r-project.org/web/packages/soundgen/vignettes/acoustic_analysis.html#visualization

<!--
### Overview

```{r, out.height=400,out.width=850}
 #https://rich-iannone.github.io/DiagrammeR/graphviz_and_mermaid.html


DiagrammeR::grViz("digraph flow {

graph [rankdir = LR]


# define the global styles of the nodes. We can override these in box if we wish
node [shape = egg, style = filled, fillcolor = Azure]
crossvalidation 

  node [shape = rectangle, style = filled, fillcolor = Azure]
  kfold LeaveOneOut

node [shape = egg, style = filled, fillcolor = Beige]
classification

  node [shape = rectangle, style = filled, fillcolor = Beige]
    Linear  SVM LDA LogReg
    NonLinear GaussianKernelSVM DeepNeuralNetwork    

node [shape = rectangle, style = filled, fillcolor = HoneyDew]
Features timeDomain freqDomain

node [shape = rectangle, style = filled, fillcolor = Linen]
EEG



# edge definitions with the node IDs
Features->{timeDomain freqDomain}
crossvalidation->{kfold LeaveOneOut}
classification->Linear->{SVM LDA LogReg}
classification->NonLinear->{GaussianKernelSVM DeepNeuralNetwork}

}") 
```

### Data workflow

```{nomnoml, echo = FALSE, out.height=400,out.width=850}
# https://cran.r-project.org/web/packages/nomnoml/readme/README.html
#fontSize: 6
#arrowSize: .5
#stroke: black
#.box: dashed center
#.comment: fill=Wheat empty bold
#.client: fill=LavenderBlush empty bold
#background: FloralWhite
#lineWidth: 1
#direction: right
#leading: .75
#lineWidth: .75
#padding: 5
#spacing: 0
#zoom: 2
#   
# [<state>user]-> local[<comment> PC |]
# [PC] --> cloud [<client>OneDrive/Sharepoint | spinco_documentation]
# [user]-> remote[<comment>Linux | 130.60.236.20 |130.60.238.20]
# [PC] -- [<database> SMB-share ]
#  
# [<database> SMB-share] <-> private [<client>gfraga | scripts]
#   [gfraga | scripts]-:> push2web [<state>github repo]
# 
# [<database> SMB-share] <->  [<client>spinco_data |raw, final outputs, long-term ]
# 
# [Linux] -- [<database> NFS-share | heavy processing]
# [Linux] -- [<database> SMB-share]
# [<database> NFS-share] <-> shared [mnt/spinco |intermediate and final outputs]
# [<database> NFS-share] <-> private [mnt/gfraga-data]
# [<database> NFS-share] <--> shared [spinco_data]
``` -->