---
title: "Digits in Noise EEG" 
abstract: "The data current experiment is used in a submited manuscript by Thomas Houweling (under review). It is set to examine associations between EEG activity and speech in noise recognition. Task requires hearing a digit name embbeded in different levels of noise and pressing the corresponding digit in a pad (digits are 1:6,8:9). <br><br> Data from N = 25 adults (after 7 subjects discarded;initial sample mean age 23.5, SD=3.9 years; 29 female)  <br><br>  Performance measures per trial are accuracy (correct/incorrect) and clarity rating (1-9 subjective scale). SNR of presentation are calibrated per individual in a pretest,  defining 3 SNR levels: SRT50 (50% correctness in calibration test), SRT-1.5db (noisier), SRT+1.5db (less noisy). <br><br> Prestimulus alpha power (8.5-12Hz) in noisy trials was higher for correct than for incorrect trials, and for those rated as clearer vs less clear. Linear mixed effect logistic regression model: accuracy ~ α power * SNR + (1|subject:digit) using source-reconstructed power found significant prediction in a left posterior temporal area in -300  to -50 ms. Interaction with stimuli difficulty: positive influence of alpha for recognizing clearer targets, but negative influence for the less clear targets." 
runhead: "A Running Head"
author:
  name: Gorka Fraga Gonzalez  [Thomas Houweling dataset]
  affiliation: University of Zurich 
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
      code_folding: hide
      highlight: espresso
      theme: spacelab
      toc: true
      toc_float:
          collapsed: false
          smooth_scroll: true
          toc_depth: 6
params:
    dirinput:  "W:/Transfer/forGorka"
        
      #self_contained: false
---

```{r, include=FALSE}
 
    knitr::opts_knit$set(root.dir = 'V:/gfraga/scripts_neulin/Projects/SINEEG')    
    knitr::opts_chunk$set(echo=TRUE,warning=FALSE)
    library(tidyr)
    library(dplyr)
   library(reactable)
    source('V:/gfraga/scripts_neulin/Projects/SINEEG/funs/eeg_funs.R')
    

    
```

```{r, include = FALSE}
options(width=60)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x,options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"',options$max.height)
    )
   hook_output(x, options)    
  })
})

```

### Description

#### Data folders

All Digits-in-noise (DiN) EEG data are to be found under 'EEG_DATA' folder under the subject's main folder (which also contains behavioral performance among others)

-   In **EEG_DATA** the '.raw' files are the raw recordings (4-6 files containing several tasks). Then, raw are saved into multiple .mat files (with parts)

-   *InterpChans.mat* file contains info about channels interpolated for later steps

-   In **'EEG_DATA/Downsampled'** the .raw files are transformed into '.set' files (different parts). It follows the main preprocessing pipeline, used in the submitted manuscript. ['Downsamp' contains changes in revision. Do not use.]

-   **'EEG_DATA/Downsampled/DiN'** contains *epoched* sets, and *epoched_ICrem* sets (after removal of IC components) as well as a *trialInfo.mat* file


#### Scripts 

- **xxx** preprocessing scripts. Each contains multiple preprocessing steps. Each script represents a 'part' in the preprocessing sequence (parts 1-3)
- **'Utils'** contains all required functions for the preprocessing scripts 
- 'BAK' contains unorganized copies of files. Ignore. 

### Folder tree {.tabset}

#### file overview

```{r, out.width='1000px'}

  # Find subdirectories
  allfiles <- dir(params$dirinput,recursive=TRUE)
  
  # get all subjects list
  subjects <- unique(sapply(strsplit(allfiles,'/'),'[',2))
  subjects <- subjects[!is.na(subjects)]
  subjects <- sort(subjects)
  sbjNewLabel<- paste0('SUBJECT_',formatC(as.numeric(sapply(strsplit(subjects,split = '_'),'[[',2)),  width = 2, format = "d", flag = "0"))

    #summary content
  tbl <-  data.frame(subjects)
  #tbl <- data.frame(matrix(nrow=length(subjects)))
  for (s in 1:length(tbl$subjects)){

  # search files for current measurement
    curfiles <- allfiles[grepl(pattern = paste0(subjects[s],'/'),allfiles)]
    tbl$subjects[s] <- sbjNewLabel[s]
    tbl$nRaw[s] <-  length(curfiles[grepl('/EEG_DATA/.*.raw',curfiles)])
    tbl$nDownsampled[s] <-  length(curfiles[grepl('/EEG_DATA/DOWNSAMPLED/.*.downsampled_merged.set',curfiles)])
    tbl$nInterpChanFiles[s] <-  length(curfiles[grepl('/EEG_DATA/DOWNSAMPLED/interpChans.mat',curfiles)])
    tbl$nEpochedSet[s] <-  length(curfiles[grepl('/EEG_DATA/DOWNSAMPLED/DiN/.*.epoched.set',curfiles)])
    tbl$nICrmSet[s] <-  length(curfiles[grepl('/EEG_DATA/DOWNSAMPLED/DiN/.*.epoched_ICrem.set',curfiles)])
  }
  tbl <- tbl[order(tbl$subjects),]
  
```


Total N = `r nrow(tbl)` 

Valid N = `r length(which(tbl$nICrmSet!=0))` [epoched_ICrem files found]

```{r, out.width='1000px'}
  reactable(tbl,filterable = TRUE,
                        defaultColDef = colDef( align = "center", minWidth = 70,headerStyle = list(background = "#f7f7f8")),
                        bordered = TRUE, highlight =TRUE) 
```

#### all subfolders

```{r,max.height='600px'}
  
  # Print folder tree    
  fs::dir_tree(params$dirinput,recurse=TRUE,type='directory')

```

#### all subfolders & files

```{r, max.height = '600px' }
  fs::dir_tree(params$dirinput,recurse=TRUE)
```

